\documentclass{my_cl_class}

\newcommand{\name}[1]{
   \raggedleft{\textbf{\Large{#1}}}
   \\
   \vspace{0.10cm}
}

\newcommand{\contact}[1]{
   \raggedleft{\large{#1}}
    \\
    \vspace{0.10cm}
}



\begin{document}

\name{Harsh Patel}

\contact{275 Capron Road,}
\contact{Cocoa, FL - 32927}
\contact{E-mail : \href{mailto:hurr03@gmail.com}{hurr03@gmail.com}}
\contact{Phone : 321-877-4174 }

\vspace{0.5cm}



{\centerline{\large{\textbf{\underline{{Subject : Bioinformatics Biology Internship at Theravance Biopharma}}}}}
\vspace{0.75cm}
\raggedright{\large{Dear Hiring Manager, }}
\\
\vspace{0.40cm}
\hspace{4.0cm}
\large{Your recent post for the search of a bioinformatics intern on Glassdoor has catched my attention. Soon to graduate with a bachelor's degree in computer science along with a year's experience of learning and developing bioinformatics tools, please consider my application for this position.}

\vspace{0.30cm}
\hspace{4.0cm}
\large{Through my undergraduate studies I've become familiar with and have utilized general-purpose programming languages like C, C++, Java and Python. For the past year, I've worked with three fellow CS students to design and implement a bioinformatics pipeline for the bioinformatics cluster at my university. Through this experience, I've become comfortable with Git, Bash Scripting in UNIX, molecular biology and many bioinformatics tools. I've enjoyed working on the project so I'm currently enrolled in directed research study as an elective improving the pipeline directly with the lead of the bioinformatics cluster at my university.}

\vspace{0.30cm}
\hspace{4.0cm}
\large{I've worked as a teaching assistant for Database Management Systems where I've reinforced my knowledge of SQL and XML. One of my duties was answering students' course questions which improved my communication skills in a professional setting.}

\vspace{0.30cm}
\hspace{4.0cm}
%As I will be pursuing bioinformatics for my post-graduate studies in the future, this internship would be an excellent opportunity for me to explore and further understand the bioinformatics world.
\large{ As I will be pursuing bioinformatics for my post-graduate studies in the future, this internship would be an excellent opportunity for me to explore and further understand the bioinformatics world. If you would like to talk more about my experiences, please call me at 321-877-8184 or e-mail me at \href{mailto:hurr03@gmail.com}{hurr03@gmail.com}. Thank you for your time and effort in reviewing my application.}
\\
\vspace{1.00cm}
\raggedleft{\large{Sincerely,}}
\\
\vspace{0.10cm}
\raggedleft{\large{Harsh Patel}}





\end{document}